### 2020-04-29 final_report/introduction.tex
replace accuracy with regression performance (mostly)

The input parameters of the computationally-expensive TBR model therefore fall
into two classes. Continuous parameters, including material thicknesses and
packing ratios, describe the geometry of a given reactor configuration. Discrete
categorical parameters further specify all relevant material sections, including
coolants, armours, and neutron multipliers. One notable exception is the
enrichment ratio, a continuous parameter denoting the presence of
\isotope[6]{Li}. Our challenge, put simply, was to produce a TBR function which
takes these same input parameters and approximates the MC TBR model with the
greatest achievable accuracy.

>>>>

The input parameters of the computationally-expensive TBR model therefore fall
into two classes. Continuous parameters, including material thicknesses and
packing ratios, describe the geometry of a given reactor configuration. Discrete
categorical parameters further specify all relevant material sections, including
coolants, armours, and neutron multipliers. One notable exception is the
enrichment ratio, a continuous parameter denoting the presence of
\isotope[6]{Li}. Our challenge, put simply, was to produce a TBR function which
takes these same input parameters and approximates the MC TBR model with the
greatest achievable regression performance.

### 2020-04-29 final_report/methodology.tex
replace accuracy with regression performance (mostly)

\Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected accuracy of their predictions. In addition, we also track
relative measures that are better-suited for comparison between this work and others, as
they maintain invariance with respect to the selected domain and image space.
For complexity analysis, surrogates are assessed in terms of wall time
elapsed during training and predicition. This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for the
expensive MC TBR model. Since training set sizes remain to be determined, all times are
reported per a single datapoint. Even though some surrogates support acceleration
by means of parallelisation, measures were taken to ensure sequential
processing of samples to achieve comparability between considered
models.\footnote{The only exception to this are artificial neural networks, which are
notoriously slow to train on conventional CPU architectures in serialised
setting.}

@@

In the first experiment, efforts are made to maximise the possibility of success
in surrogates that are prone to suboptimal performance in discontinuous spaces.
This follows the notion that, if desired, accuracy of such models may be
replicated by training separate instances to model each continuous subregion of
the domain independently.
To this end, data are limited to a single slice from run~2, and discrete
features are completely withheld from evaluated
surrogates. This is repeated for each of the four available slices to
investigate variance in behaviour under different discrete feature assignments.

>>>>

\Cref{tbl:metrics} provides an exhaustive listing and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected uncertainty of their predictions. In addition, we also track
relative measures that are better-suited for comparison between this work and others, as
they maintain invariance with respect to the selected domain and image space.
For complexity analysis, surrogates are assessed in terms of wall time
elapsed during training and predicition. This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for the
expensive MC TBR model. Since training set sizes remain to be determined, all times are
reported per a single datapoint. Even though some surrogates support acceleration
by means of parallelisation, measures were taken to ensure sequential
processing of samples to achieve comparability between considered
models.\footnote{The only exception to this are artificial neural networks, which are
notoriously slow to train on conventional CPU architectures in serialised
setting.}

@@

In the first experiment, efforts are made to maximise the possibility of success
in surrogates that are prone to suboptimal performance in discontinuous spaces.
This follows the notion that, if desired, performance of such models may be
replicated by training separate instances to model each continuous subregion of
the domain independently.
To this end, data are limited to a single slice from run~2, and discrete
features are completely withheld from evaluated
surrogates. This is repeated for each of the four available slices to
investigate variance in behaviour under different discrete feature assignments.

### 2020-04-29 final_report/results.tex
replace accuracy with regression performance (mostly)

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and artificial neural networks offer the best accuracy on
larger sets overall. This is a curious extension of the previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.

>>>>

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and artificial neural networks offer the best regression performance on
larger sets overall. This is a curious extension of the previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.
